### 2015-04-06 cug_paper/04_futurework.tex
Paper: fix a spelling error

Another feature the authors would like to add is the ability to use regular system RAM in addition to the GPU RAM.  It is well known that some applications do not use all the RAM on the compute node.  It is debatable whether letting the daemon use the memory is better than simply letting the operating system use it as  Lustre client cache or OS page cacher.  However, as was discussed in Section \ref{sec:analysis} and Section \ref{sec:conclusion}, the Lustre client-side cache has fairly low limits on the amount of dirty pages it will allow.  (The Linux kernel page cache has similar low limits on dirty pages.)  Some very basic initial testing implies that allowing the daemon to allocate memory may be more useful than letting the OS use the same memory for page cache, but further testing is required to be certain.

>>>>

Another feature the authors would like to add is the ability to use regular system RAM in addition to the GPU RAM.  It is well known that some applications do not use all the RAM on the compute node.  It is debatable whether letting the daemon use the memory is better than simply letting the operating system use it as  Lustre client cache or OS page cache.  However, as was discussed in Section \ref{sec:analysis} and Section \ref{sec:conclusion}, the Lustre client-side cache has fairly low limits on the amount of dirty pages it will allow.  (The Linux kernel page cache has similar low limits on dirty pages.)  Some very basic initial testing implies that allowing the daemon to allocate memory may be more useful than letting the OS use the same memory for page cache, but further testing is required to be certain.
